Figures

### 2016-01-21 scripts/figures.Rmd
some table formatting

## Figure 1

@@

m.roc.table$Frequency<-c("5.0%","2.5%","1.25%","0.63%","0.016%")
m.roc.table$Sensitivity<-round(m.roc.table$Sensitivity,digits=3)
m.roc.table$Specificity<-round(m.roc.table$Specificity,digits=3)

tbl<-tableGrob(m.roc.table,rows=NULL,theme=ttheme_minimal()) # Make table

@@

#plot_grid(miseq.setup,miseq.roc.p, tbl, labels=c("A", "B","C"), ncol = 3, nrow = 1)
# Figure 2
ggdraw() +
  draw_plot(miseq.setup, 0, .5, .5, .5) +
  draw_plot(miseq.roc.p, .5, .5, .5, .5) +
  draw_plot(tbl, 0, 0, 1, .5) +
  draw_plot_label(c("A", "B", "C"), c(0, 0.5, 0), c(1, 1, 0.5), size = 15)

@@

h.table.df<-subset(h.table.df,gc==5,select=-c(gc))
h.table.df$Frequency<-c("5.0%","2.0%","1.0%","0.5%","0.2%")
h.table.df$Sensitivity<-round(h.table.df$Sensitivity,digits=3)
h.table.df$Specificity<-round(h.table.df$Specificity,digits=3)

@@

read.roc<-ggplot(subset(h.cut.read.df,gc==5),aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_manual(values=rhg_cols,name="Frequency",labels=c("5.0%","2.0%","1.0%","0.5%","0.2%"))+xlab(bquote("1-Specificity (x"~10^-3~")"))+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(0,0.005),breaks=c(0,0.001,0.002,0.003,0.004,0.005),labels=c(0:5))+theme(legend.position="none")

@@

h.cut.read.table.5<-subset(h.cut.read.table,gc==5,select=-c(gc))
rename(h.cut.read.table.5,c("exp.freq"="Frequency","adj.sensitivity"="Sensitivity","TP"="True Positives","adj.specificity"="Specificity","FP"="False Positives"))->h.cut.read.table.5
h.cut.read.table.5$Frequency<-c("5.0%","2.0%","1.0%","0.5%","0.2%")
h.cut.read.table.5$Sensitivity<-round(h.cut.read.table.5$Sensitivity,digits=3)
h.cut.read.table.5$Specificity<-round(h.cut.read.table.5$Specificity,digits=3)

@@

```{r,roc_lower_inputs4}
roc.4<-ggplot(subset(h.cut.read.df,gc==4),aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_manual(values=rhg_cols,name="Frequency",labels=c("5.0%","2.0%","1.0%","0.5%","0.2%"))+xlab(bquote("1-Specificity (x"~10^-3~")"))+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(0,0.005),breaks=c(0,0.001,0.002,0.003,0.004,0.005),labels=c(0:5))+theme(legend.position="none")

@@

roc.3<-ggplot(subset(h.cut.read.df,gc==3),aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_manual(values=rhg_cols,name="Frequency",labels=c("5.0%","2.0%","1.0%","0.5%","0.2%"))+xlab(bquote("1-Specificity (x"~10^-3~")"))+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(0,0.005),breaks=c(0,0.001,0.002,0.003,0.004,0.005),labels=c(0:5))+theme(legend.position="none")

@@

h.cut.read.table.4<-subset(h.cut.read.table,gc==4,select=-c(gc))
rename(h.cut.read.table.4,c("exp.freq"="Frequency","adj.sensitivity"="Sensitivity","TP"="True Positives","adj.specificity"="Specificity","FP"="False Positives"))->h.cut.read.table.4
h.cut.read.table.4$Frequency<-c("5.0%","2.0%","1.0%","0.5%","0.2%")
h.cut.read.table.4$Sensitivity<-round(h.cut.read.table.4$Sensitivity,digits=3)
h.cut.read.table.4$Specificity<-round(h.cut.read.table.4$Specificity,digits=3)

@@

h.cut.read.table.3<-subset(h.cut.read.table,gc==3,select=-c(gc))
rename(h.cut.read.table.3,c("exp.freq"="Frequency","adj.sensitivity"="Sensitivity","TP"="True Positives","adj.specificity"="Specificity","FP"="False Positives"))->h.cut.read.table.3
h.cut.read.table.3$Frequency<-c("5.0%","2.0%","1.0%")
h.cut.read.table.3$Sensitivity<-round(h.cut.read.table.3$Sensitivity,digits=3)
h.cut.read.table.3$Specificity<-round(h.cut.read.table.3$Specificity,digits=3)

@@

dups.roc.p<-ggplot(dups.roc,aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_manual(values=rhg_cols,name="Frequency",labels=c("5.0%","2.0%","1.0%","0.5%","0.2%"))+xlab(bquote("1-Specificity (x"~10^-3~")"))+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(0,0.005),breaks=c(0,0.001,0.002,0.003,0.004,0.005),labels=c(0:5))+theme(legend.position="none")

@@

rename(dups.table,c("exp.freq"="Frequency","adj.sensitivity"="Sensitivity","TP"="True Positives","adj.specificity"="Specificity","FP"="False Positives"))->dups.table
subset(dups.table,select=-c(gc))->dups.table
dups.table$Frequency<-c("5.0%","2.0%","1.0%","0.5%")
dups.table$Sensitivity<-round(dups.table$Sensitivity,digits=3)
dups.table$Specificity<-round(dups.table$Specificity,digits=3)

>>>>

dd=4 # digits in tables
```

> make sure the possible fp accounts for the fact that we aren't looking at the priming regions for both Miseq and Hiseq
## Figure 1

@@

m.roc.table$Frequency<-c("5.0%","2.5%","1.25%","0.63%","0.016%")
m.roc.table$Sensitivity<-round(m.roc.table$Sensitivity,digits=dd)
m.roc.table$Specificity<-round(m.roc.table$Specificity,digits=dd)

tbl<-tableGrob(m.roc.table,rows=NULL,theme=ttheme_minimal()) # Make table
tbl<-gtable_add_grob(tbl,
        grobs = segmentsGrob( # line across the bottom
            x0 = unit(0,"npc"),
            y0 = unit(0,"npc"),
            x1 = unit(1,"npc"),
            y1 = unit(0,"npc"),
            gp = gpar(lwd = 2.0)),
        t = 1, b = 1, l = 1, r = ncol(tbl))

tbl<-gtable_add_grob(tbl,
        grobs = segmentsGrob( # line across the bottom
            x0 = unit(0,"npc"),
            y0 = unit(0,"npc"),
            x1 = unit(0,"npc"),
            y1 = unit(0,"npc"),
            gp = gpar(lwd = 2.0)),
        t = 1, b = 1, l = 1, r = ncol(tbl))

@@

#plot_grid(miseq.setup,miseq.roc.p, tbl, labels=c("A", "B","C"), ncol = 3, nrow = 1)
# Figure 2
ggdraw() +
  draw_plot(miseq.setup, 0.01, .53, .45, .42) +
  draw_plot(miseq.roc.p, .5, .5, .45, .45) +
  draw_plot(tbl, 0, 0, 1, .5) +
  draw_plot_label(c("A", "B", "C"), c(0, 0.5, 0), c(1, 1, 0.5), size = 15)

@@

h.table.df<-subset(h.table.df,gc==5,select=-c(gc))
h.table.df$Frequency<-c("5.0%","2.0%","1.0%","0.5%","0.2%")
h.table.df$Sensitivity<-round(h.table.df$Sensitivity,digits=dd)
h.table.df$Specificity<-round(h.table.df$Specificity,digits=dd)

@@

read.roc<-ggplot(subset(h.cut.read.df,gc==5),aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_manual(values=rhg_cols,name="Frequency",labels=c("5.0%","2.0%","1.0%","0.5%","0.2%"))+xlab(bquote("1-Specificity (x"~10^-3~")"))+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(0,0.0025),breaks=c(0,0.001,0.002),labels=c(0:2))+theme(legend.position="none")

@@

h.cut.read.table.5<-subset(h.cut.read.table,gc==5,select=-c(gc))
rename(h.cut.read.table.5,c("exp.freq"="Frequency","adj.sensitivity"="Sensitivity","TP"="True Positives","adj.specificity"="Specificity","FP"="False Positives"))->h.cut.read.table.5
h.cut.read.table.5$Frequency<-c("5.0%","2.0%","1.0%","0.5%","0.2%")
h.cut.read.table.5$Sensitivity<-round(h.cut.read.table.5$Sensitivity,digits=dd)
h.cut.read.table.5$Specificity<-round(h.cut.read.table.5$Specificity,digits=dd)

@@

```{r,roc_lower_inputs4}
roc.4<-ggplot(subset(h.cut.read.df,gc==4),aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_manual(values=rhg_cols,name="Frequency",labels=c("5.0%","2.0%","1.0%","0.5%","0.2%"))+xlab(bquote("1-Specificity (x"~10^-3~")"))+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(0,0.0025),breaks=c(0,0.001,0.002),labels=c(0:2))+theme(legend.position="none")

@@

roc.3<-ggplot(subset(h.cut.read.df,gc==3),aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_manual(values=rhg_cols,name="Frequency",labels=c("5.0%","2.0%","1.0%","0.5%","0.2%"))+xlab(bquote("1-Specificity (x"~10^-3~")"))+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(0,0.0025),breaks=c(0,0.001,0.002),labels=c(0:2))+theme(legend.position="none")

@@

h.cut.read.table.4<-subset(h.cut.read.table,gc==4,select=-c(gc))
rename(h.cut.read.table.4,c("exp.freq"="Frequency","adj.sensitivity"="Sensitivity","TP"="True Positives","adj.specificity"="Specificity","FP"="False Positives"))->h.cut.read.table.4
h.cut.read.table.4$Frequency<-c("5.0%","2.0%","1.0%","0.5%","0.2%")
h.cut.read.table.4$Sensitivity<-round(h.cut.read.table.4$Sensitivity,digits=dd)
h.cut.read.table.4$Specificity<-round(h.cut.read.table.4$Specificity,digits=dd)

@@

h.cut.read.table.3<-subset(h.cut.read.table,gc==3,select=-c(gc))
rename(h.cut.read.table.3,c("exp.freq"="Frequency","adj.sensitivity"="Sensitivity","TP"="True Positives","adj.specificity"="Specificity","FP"="False Positives"))->h.cut.read.table.3
h.cut.read.table.3$Frequency<-c("5.0%","2.0%","1.0%")
h.cut.read.table.3$Sensitivity<-round(h.cut.read.table.3$Sensitivity,digits=dd)
h.cut.read.table.3$Specificity<-round(h.cut.read.table.3$Specificity,digits=dd)

@@

dups.roc.p<-ggplot(dups.roc,aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_manual(values=rhg_cols,name="Frequency",labels=c("5.0%","2.0%","1.0%","0.5%","0.2%"))+xlab(bquote("1-Specificity (x"~10^-3~")"))+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(0,0.001),breaks=c(0,0.0005,0.001),labels=c(0,0.5,1))+theme(legend.position="none")

@@

rename(dups.table,c("exp.freq"="Frequency","adj.sensitivity"="Sensitivity","TP"="True Positives","adj.specificity"="Specificity","FP"="False Positives"))->dups.table
subset(dups.table,select=-c(gc))->dups.table
dups.table$Frequency<-c("5.0%","2.0%","1.0%","0.5%")
dups.table$Sensitivity<-round(dups.table$Sensitivity,digits=dd)
dups.table$Specificity<-round(dups.table$Specificity,digits=dd)
